\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{// All comments are NOT created equal}

### 2014-12-05 Proposal.tex
happy up to 4.4

Information can be (re)presented in different ways: text, visuals, images, etc. Actually everything that is in the world around us conveys information to us. A sign of a women on a door conveys to most of us that this is a bathroom for women. The information graphs that OMDoc provides us with could also be simply visualized as a tree of information. But this would not be very engaging and it would be hard for a human to process. Similarly traditional slide-based presentations do not provide a very engaging or interactive form of presenting information. \\

In the proposed research we will focus less on text, tree-like structures, metaphors, or semiotics like the sign of a woman on a door. We will rather focus on the spatial narrative and placing content that inherently belongs together visually close together since this can convey the meaning that these objects belong together.\\

@@

The figure \ref{fig:Objects} above clarifies what we mean by 'meaningful representations'. Figure \ref{fig:imp_objects} shows how size conveys importance. It is well known that people tend to identify the circle on the right as most important, the ones on the left are less important due to their relative size. Considering the relation of the three circles most people say that the two circles on the left belong together whereas the circle on the right is clearly something different. When shown Figure \ref{fig:rel_objects} they quickly change their mind and say that they are now actually related.\\

These perceptions can be used to convey meaning visually. For the example of Annie this means that the \textit{course-new} information would likely be important and therefore bigger than the \textit{content-old} or \textit{content-ancient} information. From there on it depends how important the topics related to this topic are and we will use different sizes to differentiate between more important and less important topics. Similarly we will employ visual relations as in \ref{fig:rel_objects} to show related content. Thus we will provide Annie with a meaningful representation of the information taken from the information graph. In turn this should allow Annie to absorb information about importance and relations instinctively which improves knowledge transfer.\\

>>>>

Information can be (re)presented in different ways: text, visuals, images, etc. Actually everything that is in the world around us conveys information to us. A sign of a women on a door conveys to most of us that this is a bathroom for women. The information graphs that OMDoc provides us with could also be simply visualized as a tree of information. But this would not be very engaging and it would be hard for a person to process. Similarly, traditional slide-based presentations do not provide a very engaging or interactive form of presenting information. \\

In the proposed research we will focus less on text, tree-like structures, metaphors, or semiotics, like the sign of a woman on a door. We will rather focus on the spatial narrative and placing content that inherently belongs together visually close together since this can convey the meaning that these objects belong together.\\

@@

The figure \ref{fig:Objects} above clarifies what we mean by 'meaningful representations'. Figure \ref{fig:imp_objects} shows how size conveys importance. It is well known that people tend to identify the circle on the right as most important, the ones on the left are less important due to their relative size. Considering the relation of the three circles most people say that the two circles on the left belong together whereas the circle on the right is clearly something different. When shown Figure \ref{fig:rel_objects} they quickly change their mind and say that they are now actually related.\\
\newpage
\begin{wrapfigure}{l}{0.5\textwidth}
\vspace{-10pt}
  \begin{center}
  \fbox{
    \includegraphics[width=0.45\textwidth]{assets/Annie4size}
    }
  \end{center}
\vspace{-20pt}
  \caption{Relative size and relations}
  \label{fig:Annie-relsize}
\vspace{-10pt}
\end{wrapfigure}

These perceptions can be used to convey meaning visually. For the example of Annie this means that the \textit{course-new} information would likely be important and therefore bigger than the \textit{content-old} or \textit{content-ancient} information. Then, it depends on how important the topics related to this topic are and we will use different sizes to differentiate between more important and less important topics. Similarly we will employ visual relations as in figure \ref{fig:rel_objects} to show related content. Considering figure \ref{fig:Annie-ancient}, we already have different sizes based on the relatedness of the concepts. Adding on to that in figure \ref{fig:Annie-relsize}, we have nodes that represent concepts that are very important for the course, here the next topic, represented as bigger. Thus we will provide Annie with a meaningful representation of the information taken from the information graph. In turn this should allow Annie to absorb information about importance and relations instinctively which improves knowledge transfer.\\
